The \project{unRAVE} catalog of X.X million detailed stellar abundances for chemodynamic studies

### 2016-08-16 article/unrave.tex
githash ftw

@@

% TODO: Replace ZENODO-URL with a data url
Source code for this project is available at \texttt{\url{https://www.github.com/AnnieJumpCannon/RAVE}}.  This document was compiled from revision hash \githash\
in that repository.
Inferred labels and covariance matrices are available with associated metadata electronically at \texttt{\url{ZENODO-URL}}.  Please note that it is a condition of using these results that the fifth \rave\ data release by \citet{Kunder_2016} must (also) be cited, as the work presented here would not have been possible without the tireless efforts of the entire \rave\ collaboration, past and present.

>>>>

\input{vc.tex}

@@

% TODO: Replace ZENODO-URL with a data url
Source code for this project is available at \texttt{\url{https://www.github.com/AnnieJumpCannon/RAVE}}.  
This document was compiled from revision hash \texttt{\githash} in that repository.
Inferred labels and covariance matrices are available electronically with 
associated metadata at \texttt{\url{ZENODO-URL}}.  Please note that it is a condition
of using these results that the fifth \rave\ data release by \citet{Kunder_2016} 
must (also) be cited, as the work presented here would not have been possible 
without the tireless efforts of the entire \rave\ collaboration, past and present.
